Windowed least-squares model reduction for dynamical systems

### 2019-10-14 section4/numerical_methods.tex
thru 4.1

\section{Numerical solution techniques}\label{sec:numerical_techniques}
The discussion to this point has outlined the formulation of the \methodAcronym\ method. We now consider numerical solution techniques. 
\methodAcronym\ displays commonalities with optimal
control problems, and as such a large existing body of work can be leveraged. In this section we 
outline a variety of such techniques. We focus primarily on 
%\KTC{earlier we kept
%saying 
%direct (i.e.,
%	discretize-then-optimize) and indirect (i.e., optimize-then-discretize).
%	Let's be consistent when we re-introduce it here.}
direct (discretize-the-optimize) and indirect (optimize-then-discretize) for \spatialAcronym\ trial subspaces, 
and then briefly outline direct and indirect methods for \spaceTimeAcronym\ trial subspaces.

\subsection{\spatialAcronym: direct and indirect methods}
Numerical techniques to
solve optimal control problems can be classified as either
\textit{direct} or \textit{indirect}
methods~\cite{conway_optimalcontrolreview}. Rather than working with the first order optimality conditions~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_bcs}, direct methods ``directly" solve the optimization problem~\eqref{eq:tclsrm} by first
numerically discretizing the system and objective functional and ``transcribing"
the infinite dimensional problem into a finite-dimensional nonlinear
programming (optimization) problem. Direct approaches thus ``discretize-then-optimize".
Indirect methods, on the other hand, compute solutions to the Euler--Lagrange equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_bcs} (which comprise the first order optimality conditions of the objective functional). Thus, indirect methods ``optimize-then-discretize," and solve the optimization problem
``indirectly". A variety of discretization/solution techniques are possible for both direct and indirect methods. Collocation methods,
finite elements, spectral methods, shooting methods, etc., are all examples of
plausible solution techniques.

In the present context, we investigate both direct and indirect methods to solve \methodAcronym\ with \spatialAcronym\ trial
subspaces. We consider: 
\begin{itemize} \item \textit{Direct methods (discretize-then-optimize)}: A direct approach leveraging linear multistep methods to directly solve the optimization problem~\eqref{eq:tclsrm}.
\item \textit{Indirect methods (optimize-then-discretize)}: An indirect approach leveraging the forward--backward sweep algorithm to solve the Euler--Lagrange equations~\eqref{eq:lspg_continuous}-\eqref{eq:lspg_bcs}.

\end{itemize} 
We emphasize that a variety of other approaches exist. Future work will comprise a detailed exploration
of additional approaches.
Section~\ref{sec:direct} outlines a direct solution approach based on linear
multistep methods, while Section~\ref{sec:indirect} outlines an indirect
solution approach based on the forward--backward sweep algorithm.

>>>>

\section{Numerical solution techniques}\label{sec:numerical_techniques}
Given the formulation of the \methodAcronym\ method presented in Section
\ref{sec:tclspg}, we now consider numerical-solution techniques for the method. 
Due to the commonalities that the \methodAcronym\ method exhibits with
optimal-control problems, \KTC{is this only for S-reduction subspaces? If so,
state this.} the derivation of these techniques can leverage a large existing
body of work. In this section, we outline a variety of such techniques. We
focus primarily on 
direct (i.e., discretize-the-optimize) and indirect (i.e., optimize-then-discretize) for \spatialAcronym\ trial subspaces, 
and then briefly outline direct and indirect methods for \spaceTimeAcronym\ trial subspaces.

\subsection{\spatialAcronym: direct and indirect methods}
Numerical techniques to
solve optimal-control problems can be classified as either
\textit{direct} or \textit{indirect}
methods~\cite{conway_optimalcontrolreview}. Rather than working with the first order optimality conditions~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_bcs}, direct methods ``directly" solve the optimization problem~\eqref{eq:tclsrm} by first
numerically discretizing the system and objective functional and ``transcribing"
the infinite dimensional problem into a finite-dimensional nonlinear
programming (optimization) problem. Direct approaches thus
``discretize-then-optimize''.
In contrast, indirect methods compute solutions to the Euler--Lagrange equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_bcs} (which comprise the first-order optimality conditions of the objective functional). Thus, indirect methods ``optimize-then-discretize," and solve the optimization problem
``indirectly". A variety of both discretization/solution \KTC{why are these
lumped together? Could we just say ``discretization'', ``solution'', or
``discretization and solutin''?} techniques are possible
for both direct and indirect methods. Collocation methods,
finite-element methods, spectral methods, and shooting methods are all examples of
plausible solution techniques.

In the present context, we investigate both direct and indirect methods to solve \methodAcronym\ with \spatialAcronym\ trial
subspaces. In particular, we consider:
\begin{itemize} \item \textit{Direct methods (discretize-then-optimize)}: A direct approach leveraging linear multistep methods to directly solve the optimization problem~\eqref{eq:obj_gen_slab}.
Section~\ref{sec:direct} outlines this approach.
\item \textit{Indirect methods (optimize-then-discretize)}: An indirect
	approach leveraging the forward--backward sweep algorithm to solve the
		Euler--Lagrange equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_bcs}.
Section~\ref{sec:indirect} outlines this technique.
\end{itemize} 
We note that a variety of other approaches exist, and their investigation
comprises the subject of future work.
